---
title: "Simple document"
author: "Lauren Holley"
output: html_document
---
   `html_document:`
   ` toc: True`
    `toc_float: True`
    
    `word_document`
    
I'm an R Markdown document! 

# Section 0: libraries

```{r}
library(tidyverse)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble

"option command i" to create more code chunk

```{r}
plot_df =
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )
```

# Section 4: plots

These are plots from our random sample

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

# Section 5: Learning Assessment 2

Learning assessment: Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

This plot shows the distribution of the absolute value of $X \sim N(1, 1)$ 

```{r}
set.seed(0)

la_df =
  tibble(
    num_var = rnorm(n = 500, mean = 1),
    log_var = num_var > 0,
    abs_var = abs(num_var)
  )

ggplot(la_df, aes(x = abs_var)) + geom_histogram()
```

log_var is a logical vector returning true or false

The median is `r round(median(pull(la_df, num_var)),2)`

# Section 6: Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: Learning Assessment 3

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* The median is: `r round(median(pull(la_df, num_var)),2)`

* The mean is: `r round(mean(pull(la_df, num_var)),2)`

* The standard deviation is: `r round(sd(pull(la_df, num_var)),2)`
